Soss

### 2020-01-05 paper/paper.tex
edits

This is problematic, since we clearly need code generation to depend on the model itself. To address this, \jl#GeneralizedGenerated# includes facilities for lifting Julia values to the type level.

Using this, the type of a Soss model is \jl#Model{A,B,M}#, where 
\begin{itemize}
    \item \jl#A# gives the type of the \emph{arguments} (\jl#A=NamedTuple{T}# for some tuple of symbols \jl#T#),
    \item \jl#B# is a type-level representation of the \emph{body}, and
    \item \jl#M# is a type-level representation of the \emph{module} in which the model was defined.
\end{itemize}

>>>>

This \emph{staged compilation} introduces some additional overhead on the first call on a given argument type, due to generation and compilation of specialized code. Subsequent calls on this same type have no such overhead, and generally benefit from specialization. To acheive a net gain from this requires making enough function calls to offset the cost of code generation. This makes the approach a natural fit for the PPL domain, where long-running tight loops are very common.

However, the requirement that the generated code only depends on the types presents a challenge, since we clearly need it to depend on the model itself. To address this, \jl#GeneralizedGenerated# includes facilities for lifting Julia values to the type level.

The type of a Soss model is thus \jl#Model{A,B,M}#, where 
\begin{itemize}
    \item \jl#A# gives the type of the \emph{arguments} (\jl#A=NamedTuple{T}# for some tuple of symbols \jl#T#),
    \item \jl#B# is a type-level representation of the \emph{body}, and
    \item \jl#M# is a type-level representation of the \emph{module} in which the model was defined.
\end{itemize}
